#Load necessary library
```{r}
library(dplyr)
library(tidyr)
```

##Read activity file
```{r}
activity_labels <- read.csv("UCI HAR Dataset/activity_labels.txt", header=F, 
                            col.names = c("idactivity", "activity"), sep = "")
```

##Read feature file
```{r}
features <- read.csv("UCI HAR Dataset/features.txt", header=F, 
                         col.names = c("id", "label"), sep = "")
```


##Read train and test file with measures
```{r}
dsx <- rbind(
  read.csv("UCI HAR Dataset/train/X_train.txt", header=F, sep=""),  
  read.csv("UCI HAR Dataset/test/X_test.txt", header=F, sep="")
)
```

##rename de columns
```{r}
colnames(dsx) <- t(features$label)
```

##keep just mean and std measures
```{r}
dsx <- dsx[,grepl("mean\\(\\)|std\\(\\)|activity|subject", colnames(dsx))]
```


##read the activity for each row from dsx
```{r}
dsy <- rbind(
  read.csv("UCI HAR Dataset/train/y_train.txt", header=F, sep="", col.names = "idactivity"),
  read.csv("UCI HAR Dataset/test/y_test.txt", header=F, sep="", col.names = "idactivity")
)
```

##combine Y with the name of activity
```{r}
dsy <- merge(dsy, activity_labels, by = "idactivity")
```


#read the file that contain the subject from each row of dsx
```{r}
dssubject <- rbind(
  read.csv("UCI HAR Dataset/train/subject_train.txt", header=F, sep="", col.names = 'subject'),
  read.csv("UCI HAR Dataset/test/subject_test.txt", header=F, sep="", col.names = 'subject')
)
```

  
##combine all datasets to create a new one
```{r}
ds <- cbind(dssubject, dsy, dsx)
```


##create a tidy dataset to analyse and calculate mean for all measures
```{r}
ds_independent <- ds %>% group_by(subject, activity) %>% summarise_all(funs (mean))
```




